Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-17 doc/manuscript/ESSDmanuscript.Rmd
add C variable mapping figure

**Figure: schematic illustrating fluxes in and out of each pool**

>>>>

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory CO2 fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year)."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_variable_mapping.png")
```

### 2021-06-17 doc/manuscript/ESSDmanuscript.tex
add C variable mapping figure

\textbf{Figure: schematic illustrating fluxes in and out of each pool}

@@

\begin{figure}[H]
\includegraphics[width=12cm]{figures_tables/ForC_updates_placeholder_fig} \caption{Table of changes to ForC fields (placeholder) }\label{fig:unnamed-chunk-1}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=12cm]{figures_tables/C_variable_mapping} \caption{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory CO2 fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year).}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=12cm]{figures_tables/ForC_updates_placeholder_fig} \caption{Table of changes to ForC fields (placeholder) }\label{fig:unnamed-chunk-2}
\end{figure}
